Analysis on Trend of Death of Shelter Residence in Toronto 

### 2025-06-21 paper/paper.qmd
fixed issue w/ axes

# Display styled table with caption
summary_table.style.set_caption("Annual Summary of Deaths in Toronto Shelters (2007–2023)") \
    .set_table_styles([
        {"selector": "caption", "props": [("caption-side", "top"), ("font-size", "110%"), ("font-weight", "bold")]},
        {"selector": "th", "props": [("text-align", "center")]},
        {"selector": "td", "props": [("text-align", "center")]}
    ]) \
    .set_properties(**{"font-family": "Cambria"}) \
    .format(na_rep="NA")
```
Based on the generated line graphs, the following conclusions can be drawn:

>>>>

# Load the data
shelter_death_data = pd.read_csv("../data/analysis_data/shelter_residences_death_analysis_data.csv")

# Order the months
month_order = ["Jan", "Feb", "Mar", "Apr", "May", "Jun",
               "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"]
shelter_death_data["month"] = pd.Categorical(
    shelter_death_data["month"], categories=month_order, ordered=True
)

# Prepare facet layout: 3 columns
years = sorted(shelter_death_data["year"].unique())
ncols = 3
nrows = (len(years) + ncols - 1) // ncols

# Set sharey=True to unify Y-axis scale across all facets
fig, axes = plt.subplots(nrows=nrows, ncols=ncols, figsize=(9, nrows * 2.5), sharey=True)
axes = axes.flatten()

# Plot each year
for i, year in enumerate(years):
    ax = axes[i]
    yearly_data = shelter_death_data[shelter_death_data["year"] == year].sort_values("month")
    ax.plot(yearly_data["month"], yearly_data["total_decedents"], color="black", linewidth=1)
    ax.scatter(yearly_data["month"], yearly_data["total_decedents"], color="pink", s=40)

    ax.set_title(str(year), fontsize=10)
    ax.set_xlabel("Month")
    ax.set_ylabel("Total Deaths")
    ax.tick_params(axis='x', rotation=45)

# Hide any unused subplots
for j in range(i + 1, len(axes)):
    fig.delaxes(axes[j])

# Add a main title
fig.suptitle("Deaths in Toronto Shelters Over Time (2007.01–2024.08)",
             fontsize=16, fontweight='bold', y=1.02)

```
Based on the generated line graphs, the following conclusions can be drawn:
